Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex

\begin{table}[H]
\centering
\begin{tabular}{c l | r l}
Plant & Benchmark                  & Time    & \\\cline{1-3}
$G_1$ & CruiseControl02            & 17\,s   & \\
$G_1$ & CruiseControl02$^\dagger$  & 46\,s   & \\
$G_2$ & SpringMassDamper           & 28\,s   & \\
$G_2$ & SpringMassDamper$^\dagger$ & \xmark  & \\
$G_2$ & SatelliteB2                & 7\,s    & \\
$G_2$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
$G_2$ & SatelliteC2                & 2\,s    & \\
$G_2$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
      & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\
      & a\_PL1\_SCH2\_IMPL2        & 538\,s  & \\
      & a\_PL1\_SCH2\_IMPL3        & 12\,s   & \\
      & a\_PL1\_SCH3\_IMPL1        & 318\,s  & \\
      & a\_PL1\_SCH3\_IMPL2        & 967\,s  & \\
      & a\_PL1\_SCH3\_IMPL3        & 9798\,s & \\
      & a\_PL1\_SCH4\_IMPL1        & 6304\,s & \\
\end{tabular}

>>>>

\begin{table}[H]
\centering
\begin{tabular}{c l | r l}
Plant & Benchmark                  & Time    & \\\cline{1-3}
$G_1$ & CruiseControl02            & 17\,s   & \\
$G_1$ & CruiseControl02$^\dagger$  & 46\,s   & \\
$G_2$ & SpringMassDamper           & 28\,s   & \\
$G_2$ & SpringMassDamper$^\dagger$ & \xmark  & \\
$G_3$ & SatelliteB2                & 7\,s    & \\
$G_3$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
$G_3$ & SatelliteC2                & 2\,s    & \\
$G_3$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
      & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\
      & a\_PL1\_SCH2\_IMPL2        & 538\,s  & \\
      & a\_PL1\_SCH2\_IMPL3        & 12\,s   & \\
      & a\_PL1\_SCH3\_IMPL1        & 318\,s  & \\
      & a\_PL1\_SCH3\_IMPL2        & 967\,s  & \\
      & a\_PL1\_SCH3\_IMPL3        & 9798\,s & \\
      & a\_PL1\_SCH4\_IMPL1        & 6304\,s & \\
\end{tabular}
